%&latex



\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}







\section*{\sc Personal Information}
\begin{list1}
    \item[] American citizen.
    \item[] Born January 7$^{th}$, 1987 in Scranton, Pennsylvania.
\end{list1}




\section*{\sc Education}

{\bf Brown University}, Providence, Rhode Island USA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}


\vspace*{.05in}
\item[] M.S., Applied Mathematics,  May 2010
\end{list1}


{\bf Carnegie Mellon University}, Pittsburgh, Pennsylvania USA\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] M.S., Mathematics,  May 2009
\item[] B.S., Mathematics, May 2009
\end{list1}
















\section*{\sc Submitted Publications}
{\it Building polyhedra by self-folding: theory and experiment}, David Gracias et. al.
Submitted,  2013. 

 \hspace{-18pt}{\it Self-assembly of mesoscale octahedral isomers},
 Shivendra Pandey et. al. Submitted,  2013.

     
\section*{\sc Papers in preparation}
 {\it Measure-valued solutions of a piecewise-deterministic Markov process limit}, Joe Klobusicky, Govind Menon, and Robert Pego.  In preparation, 2014.

 {\it \hspace{-18pt}Kinetic limits of piecewise-deterministic Markov processes}, Joe Klobusicky, Govind Menon, and Robert Pego. In preparation, 2014.

 {\it \hspace{-18pt}Kinetic limits of piecewise-deterministic Markov processes applied to grain coarsening}, Joe Klobusicky, Govind Menon, and Robert Pego. In preparation, 2014.


  












