    
\textit{ Our destiny is to live out what we think, because unless we live what we know, we do not even know it.} \hspace{160pt} -Thomas Merton

Thanks to the following people who have helped bring my thoughts to action:

To Govind Menon, for serving as my advisor for the past four years.  Thank you for your patience as I regressed, digressed, and eventually progressed as a mathematician. Your commitment to excellence and clarity will serve as an example of how to approach hard problems, in mathematics and everything else. 

To Kavita Ramanan, for serving as a thesis committee member.  Thank you for several helpful comments on queueing theory. I look forward to seeing what improvements will come from your insights.         

To Robert Pego: committee member, academic mentor, and overall mensch. For almost a decade, you have been a source of how to do things right.  Thank you for the inordinate amount of time and concern that you gave during my years in Pittsburgh. I'll remember you as someone who cared a great deal about mathematics.  I'll remember you more as someone who cared enormously about passing his knowledge to others. 

To Johnny Guzman and Nat Trask.  Thanks for letting me play numericist.  I've lumped you both together because you share many things: an openness to new ideas, an academic humbleness that has substantially changed my previous rigid perceptions on mathematics, and a good sense of humor to boot.  

 To those teachers during my upbringing who gave me encouragement.  In particular, I thank Mrs. Betti, the first person I can remember who admitted to enjoying mathematics.  I also thank Mr. Walsh, my biology teacher and golf coach, for his timeless advice in the classroom and on the course. The term ``a gentleman and a scholar" gets thrown around a lot, but you are the true embodiment of it. 

Most of all, to my family. Mom and Dad, your selflessness and love is so strong and unwavering that I often take it for granted. When I think about how unreasonably blessed I am to have parents like you, all of my problems seem petty. Thanks for everything.               

  

         
 

 

