% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Daniel C. L. Johnson}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{DanCLJohnson@gmail.com --- (585) 690-2073}


\begin{resume}

\section{EDUCATION} 	{\bf Brown University}, Providence, RI \\
			{\sl Ph.D., Applied Mathematics}, expected December 2014 \\
			{\sl Sc.M., Applied Mathematics}, May 2012 
 
 			{\bf Rensselaer Polytechnic Institute}, Troy, NY \\
			{\sl B.S., magna cum laude, Mathematics}, May 2009 

\section{RESEARCH EXPERIENCE} {\bf Dissertation Research}, Brown University, July 2012 -- Present
				\begin{itemize}\itemsep -2pt
                                \item Examined self-assembly processes using geometric models and Markov methods. 
                                  \item Synthesized information from publications across many different disciplines, including computational chemistry, Bayesian statistics, and nanotechnology.
                                  \item Developed Python modules, implementing algorithms from a variety of fields.
                                  \item Visualized computational results to demonstrate research findings.
				\end{itemize}
			      {\bf Kobe-Brown Summer Simulation School}, Kobe, Japan, August 2013
				\begin{itemize}\itemsep -2pt
                                  \item Collaborated on computing project with Kobe University students.
                                  \item Created 3D visualizations for CAVE environments using ParaView.
				\end{itemize}

\section{PROFESSIONAL EXPERIENCE} {\bf Statistical Consultant}, Pleio Health Support Systems, July 2012 -- Present 
				\begin{itemize}\itemsep -2pt
                                  \item Developed Python code to parse, clean, and analyze data from over 200,000 prescription records.
                                  \item Reduced prediction intervals for estimating yield rates of company programs by 46\% using a Bayesian generative model.
                                  \item Authored report on sampling bias in Pleio trial groups, won Bronze Medal for abstracts at Academy of Managed Care 26th Annual Meeting.
                                  \item Validated statistical methodology used by Pleio for marketing purposes. 
				\end{itemize}
                                			

\section{COMPUTING SKILLS}	{\sl Languages:} Python (with NumPy, SciPy, and matplotlib), C++, MATLAB, \LaTeX.

				{\sl Selected Scientific Algorithms:} Markov chain Monte Carlo, constrained dynamics, dynamic programming, kernel density estimation, ODE solvers.

 
\section{PUBLICATIONS} Barranca, V., Johnson, D., et al. ``Dynamics of the exponential integrate-and-fire model with slow currents and adaptation'', {\sl Journal of Computational Neuroscience,} 2014. 

			Pandey, S., Johnson, D., et al. ``Self-assembly of mesoscale isomers: The role of pathways and degrees of freedom,'' {\sl PLOS ONE,} Accepted.


\section{PERSONAL INTERESTS} 	{\bf Bayesian Sports Prediction}, February 2013 -- Present 
				\begin{itemize} \itemsep -2pt
                                  \item Designed Bayesian models for predicting NCAA Basketball and English Premier League results, implemented inference schemes in Python.  
                                \end{itemize}
                                {\bf Squash}, Brown University Squash Club, October 2010 -- Present 
				\begin{itemize}\itemsep -2pt
                                  \item Captained team to three consecutive Rhode Island Squash championships.
				\end{itemize}
                                

\end{resume}
\end{document}



%
%                {\sl Research Programmer} \hfill            Summer 1990 \\
%                Psychology Department, Rensselaer Polytechnic 
%                Institute 
%                 \begin{itemize}  \itemsep -2pt %reduce space between items
%                 \item Performed computer aided statistical analysis 
%                    of data. 
%                 \end{itemize} 
